\documentclass[10pt,a4paper,roman,english]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[margin=1in,scale=0.75,a4paper]{geometry}
\usepackage{babel}

\renewcommand*{\namefont}{\fontsize{20pt}{20pt}\mdseries\upshape}

\firstname{David Kurniadi}
\familyname{Angdinata}
\email{dka316@ic.ac.uk}
\homepage{doc.ic.ac.uk/$ \sim $dka316}

\begin{document}
\makecvtitle
\vspace{-0.5in}
\section{Education}
\cventry{2016 onwards}{MEng Mathematics and Computer Science (Pure Maths and Comp Logic)}{Imperial College London}{United Kingdom}{}{First year: 83.2\%, top course student, Faculty of Engineering Dean's List, G Research Ltd Prize}
\cventry{2014 to 2015}{Singapore GCE A-level}{Temasek Junior College}{Singapore}{}{A in Mathematics, Physics, Chemistry, Project Work, Merit in NUS Modern Physics}
\cventry{2012 to 2013}{Singapore GCE O-level}{Anderson Secondary School}{Singapore}{}{A in English, Chinese, Mathematics, Additional Mathematics, Physics, Chemistry, Geography}
% \cventry{Until 2011}{Primary/Secondary}{Pelangi Kasih School}{Jakarta}{}{4-year school-based full scholarship by Singapore Ministry of Education}
\section{Employment}
\cvitem{2018 to 2019}{First year mathematics \textbf{undergraduate teaching assistant}. Weekly personal tutoring on discrete structures, logic, graphs and algorithms, and reasoning about programs.}
\cvitem{2018 summer}{\textbf{Research project on elliptic curves}. Arithmetic of elliptic curves over finite fields and rational numbers with their applications in number theory and cryptography.}
\section{Projects}
\cvitem{2018 autumn}{\textbf{Fuzzing user interface for \emph{Hypothesis}} in Python.}
\cvitem{2018 summer}{\textbf{Research project on finite projective planes}. Proved the existence and uniqueness of general planes and the non-existence or non-uniqueness of certain planes.}
\cvitem{2018 spring}{\textbf{Improvements on \emph{Pintos} operating system} in C. Improved synchronisation with thread schedulers, and implemented system calls for user programs. Group received 81\%.}
\cvitem{2017 autumn}{\textbf{\emph{WACC} language to Assembly compiler} in Haskell. Parsed syntax/semantics with Alex/Happy, and used state monads for machine code generator. Group received 94\%.}
\cvitem{}{\textbf{J P Morgan \emph{Code for Good} hackathon}. Redesigned elements of Nobel Prize website with a search engine. Front-end with Materialize CSS and back-end with Python.}
\cvitem{2017 summer}{\textbf{MIDI file parser and mechanical music player}. Parsed MIDI music files into Raspberry Pi, played music on glockenspiel through robot arms. Group placed $ 4^{th} $.}
\cvitem{2017 spring}{\textbf{Imperial College \emph{ICHack17} hackathon}. Used Microsoft Face API for Android app in Java. Played suitable music for detected facial emotions.}
\cvitem{2016 autumn}{\textbf{Research project on home robotics}. Explored modern methods of localisation, navigation, object recognition, and grasping and manipulation of home robots.}
\cvitem{}{Performed data analysis of \textbf{WhatsApp group chats} in Haskell.}
\cvitem{2012 onwards}{Solved 180 \textbf{\emph{Project Euler}} problems in Java and Haskell.}
\cvitem{2009 \& 2011}{Designed simple product website for \textbf{\emph{MiGi glass industry}} in PHP and MySQL.}
\section{Activities}
% \cvitem{2014}{Seven-week course on linear algebra, vector calculus, and differential equations.}
\cvitem{2013 to 2014}{Bronze in interschool mathematics challenge on an optimisation problem.}
\cvitem{}{Champion and team award in interschool mathematics and science quiz.}
\cvitem{}{Distinction in annual Singapore Youth Festival arts competition choir section.}
\cvitem{2012 to 2013}{Two distinctions in regional Australian Mathematics Competition.}
\cvitem{}{Gold and school award in regional SASMO mathematics olympiad.}
\cvitem{}{Voluntary weekly environmental cleaning in Waterways Watch Society Singapore.}
\section{Miscellaneous}
\cvitem{Programming}{Proficient in Haskell, LaTeX. Experienced in Java, Python, C, PHP/SQL, XHTML/CSS.}
\cvitem{Mathematics}{Research interest in commutative algebra, algebraic number theory, algebraic geometry.}
\cvitem{Languages}{Fluent in English, Mandarin / Hokkien, Malay / Indonesian. Familiar with Japanese.}
\end{document}